Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published.

### 2023-05-21 paper.Rmd
checks and updates

---
title             : "An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "QUANTIFYING PUBLISHED REGISTERED STUDIES"
author: 
  - name          : "Eline Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/. 
abstract: |
  We quantified how many research studies registered on the Open Science Framework (OSF) are performed but never publicly shared. Examining 315 registrations revealed that 169 were research studies, of which 104 (62%) were published. For the whole population of registrations on the OSF before November 2017 we estimate 58% is published. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. It is often challenging to identify whether public registrations are published due to a lack of information in registrations. In responses to emails asking researchers why studies remained unpublished, logistics (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our project shows a substantial amount of data that researchers collect is never publicly shared. Selectively publishing studies is problematic because of the possibility that the resources used to collect the data are wasted, and if the publication of studies depend on the results their non-publication can cause bias in the scientific literature. Although it is common knowledge that researchers have studies in their filedrawer, it is extremely difficult to quantify how many studies in psychology are performed, but never published. The OSF has a policy to make all registrations public after four years. This allows us to perform the first inception cohort study on the OSF where we attempt to examine for registered studies if they end up in the scientific literature after at least 4 years. A better understanding of how many studies remain unpublished, and the reasons why researchers did not publish studies, enables researchers to seriously engage with the question how internal inefficiency in science can be reduced.

@@

The practice of selective reporting has been demonstrated in various disciplines, ranging from psychology and sociology to economics [@fanelli_positive_2010; @franco_publication_2014; @gerber_publication_2010]. It is challenging to quantify how many studies remain unpublished. The most accurate estimates come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010]. Dickersin and colleagues observed that from all 737 studies submitted to John Hopkins institutional review boards of the school of medicine and health 81% and 66% were published, respectively [@dickersin_factors_1992]. Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal. Of 293 clinical trials funded by NIH in 1979, 93% was published after a decade [@dickersin_nih_1993]. In the only inception cohort study in the social sciences we know of, Franco et al. (2014) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.

One solution to prevent the selective reporting of studies is to require researchers to register their study in a publicly accessible database. An example of such a study registry is ClinicalTrials.gov [@dickersin_evolution_2012]. The requirement to register certain types of studies does not exist in psychology. However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain [@spies_open_2013]. The OSF offers researchers the possibility to voluntarily preregister their study by specifying their hypotheses, methods, and statistical analysis plan.

One interesting aspect of preregistrations on the OSF is the fact that every registration after June 8 2015  (if not withdrawn) will be made public after an embargo period of four years^[see https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ]. This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago. It is therefore possible to use the database of preregistered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.

@@

In this project we aimed to answer four main research questions. First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years. Although this population of studies is not representative of all studies researchers perform, it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.

@@

Our third question concerns the possibility to correctly identify whether the study related to a registration is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to identify relevant studies and contact the researchers who performed the study. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not. 
Finally, while it is useful to quantify how many preregistered studies remain unpublished after four years, it is also important to understand why studies remain unpublished. The fourth aim of our study was to contacted the authors of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.

@@

*Data sources*: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API). Registrations are part of at least one associated project page on the OSF. Researchers might still work on projects four years after a registration. The final classification was based on whether the projects were public in April 2022. For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project is private. We randomly sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.

@@

*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the preregistration was made public by the researchers, and 150 for which the preregistration was made public automatically after four years ). The OSF API does not provide information about how a project has been made public. To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted. We classified OSF preregistrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public. Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project. This is not a perfect proxy, as it is possible for users to make a registration public, but to keep the associated OSF project hidden (for example, because they mistakenly believe they made the entire project public when making the registration public). When the registration and underlying project are public, we assume the registration is opened by the researchers. This assumption is more likely to hold, as only users can make underlying project pages public.

*Classifying Publication Status*: Studies can be accessible in different degrees of accessibility, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021]. We considered a study ‘published’ if the study was communicated in any form that allows other researchers to learn about the results. In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis. We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. This use of the term ‘published’ differs from other inception cohort studies (e.g., Franco et al., 2014) which limit publication to journal articles. We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.

@@

*Inclusion criteria*: After some projects were reclassified during the data analysis in total `r sum(included_after$n)` randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study. Of these, the associated project was public for `r included_after$n[1]` registrations and the associated project was closed for `r included_after$n[2]` registrations. As we are interested in estimating how many studies that were performed with the goal to publish the findings remain unpublished, registrations needed to be actual research studies where the goal of the researchers was to publish a paper. We therefore aimed to remove all registrations that were performed for practice purposes (e.g. student assignments or trial registrations), as well as all registrations that were created to archive materials after the research project was completed (e.g., some journals ask researchers to use the registration option on the OSF to create a DOI that is linked to all files associated with the project after the manuscript has been accepted for publication). Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022]. For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a preregistration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.

@@

*Identifying Publications Corresponding to Registrations*: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` articles as unpublished, and for `r table(registration_data_included$published_before_email)[4]` articles we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.

@@

For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the authors. We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished. We contacted `r contacted_researchers` researchers, `r contacted_researchers_per_group$sum[1]` authors with registrations associated with public OSF projects and `r contacted_researchers_per_group$sum[2]` researchers with registrations associated with closed OSF projects, of which `r replies_per_group$sum[1]` (`r round(100*percentage_responded$sum[1],2)`%) and `r replies_per_group$sum[2]` (`r round(100*percentage_responded$sum[2],2)`%) replied to our email with additional information to update our classification. We sent `r contacted_researchers_per_publication_status$sum[2]` email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received `r responses_per_publication_status$sum[2]` response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer [@van_elk_whats_2021], `r contacted_researchers_per_publication_status$sum[3]` emails for registrations we believed remained unpublished (and received `r responses_per_publication_status$sum[3]` responses), and `r contacted_researchers_per_publication_status$sum[4]` emails because we were uncertain if they were published or not (and received `r responses_per_publication_status$sum[4]` responses). Two additional authors replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.

@@

After updating our classification based on email responses, the publication rate in group 1 increased by 6% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1%. Sometimes a publication we found in the literature did not belong to the preregistration. If the study associated with the registration was published in another article than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, `r sum(registration_data$match == 1)` of the `r sum(registration_data$match != "-")` responses match with publications we found. For the `r sum(match_per_classification[3,2:3])` registrations we classified as unpublished, responses to the follow-up emails indicated that `r match_per_classification[3,3]` (`r round(100*match_per_classification[3,3]/sum(match_per_classification[3,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.

We received `r sum(match_per_classification[4,2:3])` responses for registrations we were uncertain about, and these follow-up emails indicated that `r match_per_classification[4,3]` (`r round(100*match_per_classification[4,3]/sum(match_per_classification[4,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.

Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the `r sum(match_per_classification[4,2:3])` registrations where we were uncertain if the study was published, `r match_per_classification[4,3]` (`r round(100*(match_per_classification[4,3]/sum(match_per_classification[4,2:3])), 2)`%) of registrations matched a paper we found. Of the `r match_per_classification[4,2]` cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their preregistration on the OSF.

@@

estimated_nonpublication <- data.frame(Group = c("Manually Opened", "Automatically Opened", "Total"),
                 Total_Number_of_Registrations = c(total_open, total_closed, total_open + total_closed),
                 Percentage_Included = c(round(included_before$mean,2), ""),
                 Included_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))),0),
                 Published = c(round(result_manual$mean,2), round(result_auto$mean,2), ""), 
                 Published_estimate = round(c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0),
                 Non_Published_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))) - c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0)
                 )
colnames(estimated_nonpublication) <- c("Group", "Registrations", "% Included", "Included", "% Published", "Published", "Not Published")
apa_table(estimated_nonpublication, digits = 0, caption = "Estimated number of published and unpublished studies registered on the OSF before November 2017.")
```

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r result_total$x` registered studies are published (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]). This sample contained an almost equal number of manually opened and automatically opened registrations. As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations. Multiplying our publications estimates by the estimated number of research studies registered on the OSF before November 2017 we see `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100 * estimated_nonpublication[3,6] / (estimated_nonpublication[3,6] + estimated_nonpublication[3,7]),2)`% of registrations are published as an article, preprint, thesis, or poster after at least four years.

@@

We see that `r round(100*result_manual[4], 2)`%, 95% CI [`r round(100*result_manual[5], 2)`; `r round(100*result_manual[6], 2)`] of all registrations that based on our proxy, were classified as manually opened by the researchers have been published. In the remaining `r 100-round(100*result_manual[4], 2)`% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that `r round(100*result_auto[4], 2)`%, 95% CI [`r round(100*result_auto[5], 2)`; `r round(100*result_auto[6], 2)`] of automatically opened registrations is published. Consequently, `r 100-round(100*result_auto[4], 2)`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

>>>>

---
title             : "An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "QUANTIFYING PUBLISHED REGISTERED STUDIES"
author: 
  - name          : "Eline Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/. 
abstract: |
  We quantified how many research studies registered on the Open Science Framework (OSF) are performed but never publicly shared. Examining 315 registrations revealed that 169 were research studies, of which 104 (62%) were published. For the whole population of registrations on the OSF before November 2017 we estimate 58% is published within at least 4 years. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. It is often challenging to identify whether public registrations are published due to a lack of information in registrations. In responses to emails asking researchers why studies remained unpublished, logistics (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our project shows a substantial amount of data that researchers collect is never publicly shared. Selectively publishing studies is problematic because of the possibility that the resources used to collect the data are wasted, and if the publication of studies depend on the results their non-publication can cause bias in the scientific literature. Although it is common knowledge that researchers have studies in their filedrawer, it is extremely difficult to quantify how many studies in psychology are performed, but never published. The OSF has a policy to make all registrations public after four years. This allows us to perform the first inception cohort study on the OSF where we attempt to examine for registered studies if they end up in the scientific literature after at least 4 years. A better understanding of how many studies remain unpublished, and the reasons why researchers did not publish studies, enables researchers to seriously engage with the question how internal inefficiency in science can be reduced.

@@

The practice of selective publication has been demonstrated in various disciplines, ranging from psychology and sociology to economics [@scheel_excess_2021; @franco_publication_2014; @gerber_publication_2010]. It is challenging to quantify how many studies remain unpublished. The most accurate estimates come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010]. Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81% and 66% were published [@dickersin_factors_1992]. Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal. Of 293 clinical trials funded by NIH in 1979 93% was published after a decade [@dickersin_nih_1993]. In the only inception cohort study in the social sciences we know of, Franco et al. (2014) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.

One solution to prevent the selective reporting of studies is to require researchers to register their study in a publicly accessible database. An example of such a study registry is ClinicalTrials.gov [@dickersin_evolution_2012]. The requirement to register certain types of studies does not exist in psychology. However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain [@spies_open_2013]. The OSF offers researchers the possibility to voluntarily register their study by specifying their hypotheses, methods, and statistical analysis plan.

One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015  (if not withdrawn) will be made public after an embargo period of four years^[see https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ]. This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago. It is therefore possible to use the database of registered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.

@@

In this project we aimed to answer four main research questions. First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years. Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.

@@

Our third question concerns the possibility to correctly identify whether the study related to a registration is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to identify relevant studies and contact the researchers who performed the study. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not. 
Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is also important to understand why studies remain unpublished. The fourth aim of our study was to contacted the researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.

@@

*Data sources*: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API). Registrations are part of at least one associated project page on the OSF. Researchers might still work on projects four years after a registration. The final classification was based on whether the projects were public in April 2022. For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project is private. We sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.

@@

*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years ). The OSF API does not provide information about how a project has been made public. To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted. We classified OSF registrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public. Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project. This is not a perfect proxy, as it is possible for users to make a registration public, but to keep the associated OSF project hidden (for example, because they mistakenly believe they made the entire project public when making the registration public). When the registration and underlying project are public, we assume the registration is opened by the researchers. This assumption is more likely to hold, as only users can make underlying project pages public.

*Classifying Publication Status*: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021]. We considered a study ‘published’ if the study was communicated in any form that allows other researchers to learn about the results. In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail). We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. This use of the term ‘published’ differs from other inception cohort studies (e.g., Franco et al., 2014) which limit publication to journal articles. We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.

@@

*Inclusion criteria*: After some projects were reclassified during the data analysis in total `r sum(included_after$n)` randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study. Of these, the associated project was public for `r included_after$n[1]` registrations and the associated project was closed for `r included_after$n[2]` registrations. As we are interested in estimating how many studies that were performed with the goal to publish the findings remain unpublished, registrations needed to be actual research studies where the goal of the researchers was to publish a paper. We therefore aimed to remove all registrations that were performed for practice purposes (e.g. student assignments or trial registrations), as well as all registrations that were created to archive materials after the research project was completed (e.g., some journals ask researchers to use the registration option on the OSF to create a DOI that is linked to all files associated with the project after the manuscript has been accepted for publication). Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022]. For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a registration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.

@@

*Identifying Publications Corresponding to Registrations*: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` registrations as unpublished, and for `r table(registration_data_included$published_before_email)[4]` registrations we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.

@@

For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the researchers. We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished. We contacted `r contacted_researchers` researchers, `r contacted_researchers_per_group$sum[1]` researchers with registrations associated with public OSF projects and `r contacted_researchers_per_group$sum[2]` researchers with registrations associated with closed OSF projects, of which `r replies_per_group$sum[1]` (`r round(100*replies_per_group$sum[1]/contacted_researchers_per_group$sum[1],2)`%) and `r replies_per_group$sum[2]` (`r round(100*replies_per_group$sum[2]/contacted_researchers_per_group$sum[2],2)`%) replied to our email with additional information to update our classification. We sent `r contacted_researchers_per_publication_status$sum[2]` email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received `r responses_per_publication_status$sum[2]` response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer [@van_elk_whats_2021], `r contacted_researchers_per_publication_status$sum[3]` emails for registrations we believed remained unpublished (and received `r responses_per_publication_status$sum[3]` responses), and `r contacted_researchers_per_publication_status$sum[4]` emails because we were uncertain if they were published or not (and received `r responses_per_publication_status$sum[4]` responses). Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.

@@

After updating our classification based on email responses, the publication rate in group 1 increased by 6% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, `r sum(registration_data$match == 1)` of the `r sum(registration_data$match != "-")` responses match with publications we found. For the `r sum(match_per_classification[3,2:3])` registrations we classified as unpublished, responses to the follow-up emails indicated that `r match_per_classification[3,3]` (`r round(100*match_per_classification[3,3]/sum(match_per_classification[3,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration. We received `r sum(match_per_classification[4,2:3])` responses for registrations we were uncertain about, and these follow-up emails indicated that `r match_per_classification[4,3]` (`r round(100*match_per_classification[4,3]/sum(match_per_classification[4,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration.

Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the `r sum(match_per_classification[4,2:3])` registrations where we were uncertain if the study was published, `r match_per_classification[4,3]` (`r round(100*(match_per_classification[4,3]/sum(match_per_classification[4,2:3])), 2)`%) of registrations matched a paper we found. Of the `r match_per_classification[4,2]` cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their registration on the OSF.

@@

estimated_nonpublication <- data.frame(Group = c("Manually Opened", "Automatically Opened", "Total"),
                 Total_Number_of_Registrations = c(total_open, total_closed, total_open + total_closed),
                 Percentage_Included = c(round(included_before$mean,2), ""),
                 Included_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))),0),
                 Published = c(round(result_manual$mean,2), round(result_auto$mean,2), ""), 
                 Published_estimate = round(c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0),
                 Non_Published_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))) - c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0)
                 )

result_population <- binom.confint(x = estimated_nonpublication[3,6], n = (estimated_nonpublication[3,6]+estimated_nonpublication[3,7]), tol = 1e-8, method = "wilson")

colnames(estimated_nonpublication) <- c("Group", "Registrations", "% Included", "Included", "% Published", "Published", "Not Published")
apa_table(estimated_nonpublication, digits = 0, caption = "Estimated number of published and unpublished studies registered on the OSF before November 2017.")

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r result_total$x` registered studies are published (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]). Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations. As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations. Multiplying our publication estimates by the estimated number of research studies registered on the OSF before November 2017 we see that `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100*result_population[4], 2)`%, of registrations are published as an article, preprint, thesis, or poster after at least four years.

@@

We see that `r round(100*result_manual[4], 2)`%, 95% CI [`r round(100*result_manual[5], 2)`; `r round(100*result_manual[6], 2)`] of all registrations that based on our proxy were classified as manually opened by the researchers have been published. In the remaining `r 100-round(100*result_manual[4], 2)`% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that `r round(100*result_auto[4], 2)`%, 95% CI [`r round(100*result_auto[5], 2)`; `r round(100*result_auto[6], 2)`] of automatically opened registrations is published. Consequently, `r 100-round(100*result_auto[4], 2)`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.
